\mytitle

### 2017-10-27 paper.tex
nits

The first problem is performance. The consensus latency of \paxos protocols is 
notoriously high and unscalable~\cite{zookeeper,glendenning2011scalable}, 
incurring high 
performance overhead for server programs. A main reason is that messages of 
traditional TCP or UDP-based \paxos protocols have to go through software 
network layers in OS kernels. For efficiency, \paxos 
protocols typically take the Multi-Paxos approach~\cite{paxos:simple}: it 
assigns one replica as the ``leader'' to invoke consensus requests, and the 
other replicas as ``backups'' to agree on requests. To agree on an input, at 
least one round-trip time (RTT) is required between the leader and a backup. 
Given that a ping RTT in LAN typically takes hundreds of \us, and that the 
request processing time of key-value store servers (\eg, \redis) is at most 
hundreds of \us, existing \paxos protocols incur high overhead in the response 
time of server programs.

@@

To quantify this bottleneck, we evaluated four traditional consensus 
protocols~\cite{zookeeper, spaxos:srds12, crane:sosp15, libpaxos} on 24-core 
hosts with 40Gbps network, and we spawned 24 concurrent consensus connections. 
As shown in Figure~\ref{fig:paxos_latency}, when changing the replica group 
size from 3 to 9, although network and CPUs were not saturated, the consensus 
latency of 3 protocols drastically increased by 105.4\% to 168.3\%, and 36.5\% 
to 63.7\% of the increase was in OS kernel.

When only one consensus connection 
was spawned, the latency increase on the number of replicas was more gentle.

@@

The second problem is that most existing \smr systems are not designed to 
support unmodified server programs. To utilize existing \smr services, 
developers often have to rewrite their code to orchestrate server programs into 
the narrowly defined interfaces provided by these \smr systems. For instance, 
to leverage ZooKeeper~\cite{zookeeper}, developers have to shoehorn their 
programs into the file IO interface defined by ZooKeeper.

>>>>

First, the consensus latency of \paxos protocols is notoriously high and 
unscalable~\cite{zookeeper,glendenning2011scalable}, incurring high 
performance overhead for server programs. A main reason is that messages of 
traditional TCP or UDP-based \paxos protocols have to go through software 
network layers in OS kernels. For efficiency, \paxos 
protocols typically take the Multi-Paxos approach~\cite{paxos:simple}: it 
assigns one replica as the ``leader'' to invoke consensus requests, and the 
other replicas as ``backups'' to agree on requests. To agree on an input, at 
least one round-trip time (RTT) is required between the leader and a backup. 
Given that a ping RTT in LAN typically takes hundreds of \us, and that the 
request processing time of key-value store servers (\eg, \redis) is at most 
hundreds of \us, existing \paxos protocols incur high overhead in the response 
time of server programs.

@@

To quantify this bottleneck, we evaluated four traditional consensus 
protocols~\cite{zookeeper, spaxos:srds12, crane:sosp15, libpaxos} on 24-core 
hosts with 40Gbps network, and we spawned 24 concurrent consensus connections. 
As shown in Figure~\ref{fig:paxos_latency}, when changing the replica group 
size from 3 to 9, although network and CPUs were not saturated, the consensus 
latency of 3 protocols drastically increased by 105.4\% to 168.3\%, and 36.5\% 
to 63.7\% of the increase was in OS kernel. When only one consensus connection 
was spawned, the latency increase on the number of replicas was more gentle.

@@

Second, most existing \smr systems are not desgined to support unmodified 
server programs. To utilize existing \smr services such as 
ZooKeeper~\cite{zookeeper}, developers often have to rewrite their code to 
shoehorn their programs into the narrowly defined state machine interfaces 
provided by these \smr systems.
